---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

@import url('https://fonts.googleapis.com/css2?family=Iansui&display=swap');

body {
  font-family: "Iansui", cursive;
  font-weight: 400;
  font-style: normal;
  color: #340089;
  background-color: #f9f6f0;
}

```

## Are tabs left open when you close your laptop lid? If so, how many?

I performed a survey to learn if people leave tabs open when closing their laptops, and how many tabs are left open.

```{r}
library(tidyverse)

cvs_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSAFWvGM0O5_YDZbj2G7mNWvVdOCiSNBRqQgxAirHoAs0grpTozh-lLZ0PfrmteC38de0EgAsnkJf8T/pub?output=csv"

logged_data <- read.csv(cvs_file)

latest_data <- logged_data %>%
  rename(tabs_open = 2,
         number_of_tabs = 3,
         course_stage = 4,
         tab_type = 5,
         sorted_status = 6,
         browser = 7,
         num_of_windows = 8)

# Usable 
plot1 <- ggplot(data = latest_data) +
  geom_bar(aes(x = tabs_open),
               fill = "#aab1ff") +
  labs(title = "Are tabs kept open when laptops are closed?",
       subtitle = "Tracking how often people leave a tab here or there open",
       caption = "Source: A very small survey",
       x = "Are tabs kept open?",
       y = "Number of times")

# Yaaa def using
plot2 <- ggplot(data = latest_data) +
  geom_bar(aes(x = number_of_tabs,
           fill = sorted_status)) +
  labs(title = "How many tabs are kept open?",
       subtitle = "Tracking how many tabs are left open if people do leave them open",
       caption = "Source: A very small survey",
       x = "Number of tabs",
       y = "Number of times")


# Chosen summary values pulled from number of tabs
mean_tabs <- mean(latest_data$number_of_tabs, na.rm = TRUE)
max_tabs <- max(latest_data$number_of_tabs, na.rm = TRUE)
min_tabs <- min(latest_data$number_of_tabs, na.rm = TRUE)


```
If tabs are left open after closing the laptop, the minimum number of tabs is `r min_tabs`, the maximum number of tabs is `r max_tabs`, and the mean number of tabs is `r mean_tabs`.

 Here are some plots that represent the data I've collected:
 
```{r} 
plot1
plot2
```
